---
title: "R Project 1 - Hello R"
author: "Obed Contreras"
date: "Due Fed 3rd"
output: 
  html_document: 
    fig_width: 5
    highlight: textmate
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

- 1846 rows. 
- **dataset** , **x** , **y**
```{r}
datasaurus_dozen  %>% 
  count(dataset)  %>%
  print(13)
```

| # | Dataset | n | 
|:--|:--|:--|
| 1 |away | 142 |
| 2 | bullseye | 142|
| 3 | circle | 142|
| 4 | dino | 142|
| 5 | dots | 142|
| 6 | h_lines | 142|
| 7 | high_lines | 142|
| 8 | slant_down | 142|
| 9 | slant_up | 142|
| 10 | star | 142|
| 11 | v_lines | 142|
| 12 | wide_lines | 142|
| 13 | x_shape | 142|


### Exercise 2

First let's plot the data in the dino dataset:

```{r plot-dino}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

And next calculate the correlation between `x` and `y` in this dataset:

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

```{r plot-star}
star_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = star_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

> plot-star outputs a five-point star whereas plot-dino outputs a prehistoric reptile. 
 
```{r cor-star}
star_data %>%
  summarize(r = cor(x, y))

```
> Correlation Coefficient (r) for plot-star is marginally bigger in comparison to plot-dino's r.

### Exercise 4

```{r}
circle_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = circle_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

```{r}
circle_data %>%
  summarize(r = cor(x, y))

```
> Unlike the coefficient correlation (r) of star_data, the r of circle_data is marginally *bigger* than the r of dino_data. 


### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

```{r}
ggplot (datasaurus_dozen, aes (x = x, y = y, color = dataset)) + 
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset, in 3 cols 
  theme(legend.position = "none")
``` 

```{r}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y)) %>%
  print(13)
```
| # | Dataset | r |
| :--: | :-- | :--: |
| 1 | away | -0.0641 |
| 2 | bullseye | -0.0686 |
| 3 | circle | -0.0683 |
| 4 | dino | -0.0645 |
| 5 | dots | -0.0603 |
| 6 | h_lines | -0.0617 |
| 7 | high_lines | -0.0685 |
| 8 | slant_down | -0.0690 |
| 9 | slant_up | -0.0686 |
| 10 | star | -0.0630 |
| 11 | v_lines | -0.0694 |
| 12 | wide_lines | -0.0666 |
| 13 | x_shape | -0.0656 |


